A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
small modification in part 1

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ruiqi Gao}
\email{gao606@purdue.edu}
\affiliation{%
  \institution{Purdue University}
  \city{Lafayette}
  \state{Indiana}
  \country{USA}
  \postcode{47901}
}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing Problem (Strip Packing) is a 2-dimensional minimization geometric optimization problem where we pack a rectangles into a unit-width bin with infinite height to minimize the packing height. In this paper we study a series of approximation algorithm for 2D Packing Problem, analyze the performance. First we will study the 2 early stage intuitive approximation algorithm designed by Coffman with approximation bound 3 and 2.7. Then we will further investigate a more advanced algorithm designed by Steinberg that have a approximation bound of 2. We will also explore some future direction of this problem in the end.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}

@@

2D Packing Problem is defined as follows: We are giving a collection of rectangles $\{R_1,R_2,R_3,\dots,R_n\}$ and a bin with fixed width and infinite height, and we need to pack all the rectangles into the bin without overlapping while minimize the total bin height\cite{baker1980orthogonal}. Without loss of generality, we can normalize the width to be 1.\par

>>>>

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ruiqi Gao$\dagger$}
\email{gao606@purdue.edu}
\affiliation{%
  \institution{Purdue University}
  \city{Lafayette}
  \state{Indiana}
  \country{USA}
  \postcode{47901}
}
\author{Aocheng Li$\dagger$}
\email{li3922@purdue.edu}
\affiliation{%
	\institution{Purdue University}
	\city{Lafayette}
	\state{Indiana}
	\country{USA}
	\postcode{47901}
}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  2D Packing (Strip Packing) problem is a 2-dimensional geometric optimization problem which a list of rectangles are packed into a unit-width bin with infinite height to minimize the packing height. In this paper, we study a series of approximation algorithm for 2D Packing Problem, analyze the performance. First we will study the 2 early stage intuitive approximation algorithm designed by Coffman with approximation bound 3 and 2.7. Then we will further investigate a more advanced algorithm designed by Steinberg that have a approximation bound of 2. We will also explore some future direction of this problem in the end.
\end{abstract}
\keywords{Approximation Algorithm, 2D packing, Strip Packing}

@@

2D Packing Problem is defined as follows: Given a collection of rectangles $\{R_1,R_2,R_3,\dots,R_n\}$ each with a size of $w_i\times h_i, 1\leq i\leq n$, and a bin with fixed width and infinite height, we wish to pack all the rectangles into the bin without overlapping while minimizing the total bin height\cite{baker1980orthogonal}. Without loss of generality, we can normalize bin width to be 1.\par
